---
title: "Eating Out"
author: "Alex Moreno"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Methods

Response variable is categorical because the question is 'did you dine out last week? yes or no'
Explanatory variable is race, it, too, is a categorical variable.
Categorical ~ Categorical is used.

Chi-squared and fisher exact tests are used.


# Descriptive summaries



## Graphical Summary


### barchart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

From analyzing the charts, each race does go out to eat more often than those that do not. The white race has the highest yes amount. The percentages are higher for eating out for each race.
