---
title: "Eating Out"
author: "Alex Moreno"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Methods

Response variable is categorical because the question is 'did you dine out last week? yes or no'
Explanatory variable is race, it, too, is a categorical variable.
Categorical ~ Categorical is used.

Chi-squared and fisher exact tests are used.


# Descriptive summaries

## Graphical Summary

### barchart

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

From analyzing the charts, each race does go out to eat more often than those that do not. The white race has the highest yes amount. The percentages are higher for eating out for each race.


## Numerical Summary

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The table shows that the white race goes out to eat the most out of the samples.

## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Chi-squared test shows that the p-value is 0.000002287 which is less than 0.05. Null hypothesis is rejected in favor of the alternative.


```{r}
fisherXY(mydata$race,mydata$eatout, printAll = TRUE)
```

There is a difference between white and other, white and black. The p-value is less than 0.05 for both of these comparisons.
Black and other are similar due to the p-value being greater than 0.05.


# Summary
Does race have to do with the amount of eating out? Yes it does in comparison with white and others and also white with black. From the analysis shown here, white tends to be the one that eats out more than the rest. The p-values from the fisher test for the white comparisons is less than 0.05. The null hypothesis is rejected in favor of the alternative. There is no differnece between black and others eating out. 